\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-09-11 jss/article.tex
discuss edits

Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis. The results of which may inform the statistician whether a more intensive (in terms of coding and computational time) but more precise method (such as MCMC) should be used. As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.

In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''. For example, in GRIMM the point estimates from the package can be substituted into the marginal distribution \ref{normalmarginal} to check whether the data marginally follow this distribution. If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.

>>>>

Due to the speed and ease of use \pkg{Rgbp} can be utilized as a method of preliminary data analysis. The results of which may inform the statistician whether a more intensive (in terms of implementation and computational time) but more precise method (such as MCMC) should be used. As the package assumes non-informative priors the results can be used as reference point to see whether implementing a more sophisticated model, perhaps with informative priors, should be used.

In addition to the built in ``method checking'' procedure the package can be used to undergo ``model checking''. For example, in GRIMM, the point estimates from the package can be substituted into the marginal distribution in Equation \ref{normalmarginal} to check whether the data marginally follow this distribution. If certain modeling assumptions have been violated a more sophisticated model can be assumed and implemented by other means.
